---
title: "Height Prediction of Children by 'GaltonFamilies' dataset"
author: "Md. Moaz Ahmed Asif"
date: "`r Sys.Date()`"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Course Project: Shiny Application and Reproducible Pitch

In this application, I predicted children's height on the basis of their gender, father & mother's height, and midparentHeight. For more information on the dataset, go through - https://rdrr.io/cran/HistData/man/GaltonFamilies.html".

The application is running on: https://moaz-ahmed-asif.shinyapps.io/Height_Prediction_by_GaltonFamilies/

ui.R, and server.R Code is stored in the following repository: https://github.com/moaz-ahmed-asif/Shiny-Application-and-Reproducible-Pitch

## Details of the data

```{r, echo = T, comment = "", message = F}
library(dplyr)
library(HistData)
data(GaltonFamilies)
head(GaltonFamilies)
```

## Data manipulation

At first, the heights were converted to meter.
```{r, echo = T, comment = ""}
newGalton <- GaltonFamilies %>% 
        mutate(father = 2.54 * father / 100,
               mother = 2.54 * mother / 100,
               midparent = 2.54 * midparentHeight / 100,
               child = 2.54 * childHeight / 100)

summary(newGalton[c("father", "mother", "midparent", "child")])
```

## Fitting a model

Then, father & mother height, gender of children, and midparent were fitted to a linear model to predict children height.
```{r, echo = T}
LM <- lm(child ~ father + mother + gender + midparent, newGalton)
```
Then, gender of children and father & mother height were taken input via radioGroupButtons, and sliderInput; midparent was calculated from the father & mother height. After that, children height is predicted and shown in the ggplot.
